---
title: "Quarto"
---

```{r Clean workspace}
#| include: false

rm(list = ls())
```

```{r List all used packages}
#| include: false

packages <- c("downlit", "xml2")
```


```{r Install missing packages}
#| include: false

install.packages(setdiff(packages, rownames(installed.packages())))
```

```{r Load packages}
#| include: false

lapply(packages, require, character.only = TRUE)
```


## Render & Review

1.  VSCode/RStudio -\> *Render* button
2.  Terminal -\> `quarto preview`
3.  Terminal -\> `quarto preview help`

## Render w/o Review

1.  Terminal -\> `quarto render`
2.  Terminal -\> `quarto render help`

## Import Content

To import the content of a Quarto document into another, use the following shortcodes:

``` markdown
<!-- {{< include file.qmd >}} -->
```

## Publish Options on GitHub Pages

A summary of the publish options of a Quarto website on GitHub pages is [here (GSheet)](https://docs.google.com/spreadsheets/d/1efz-KlHgNicp8T8Kzt5ELlX6i0pvwFerosTHLgGwW_Y/preview)


## References

-   [Quarto Reference](https://quarto.org/docs/reference/)
