---
title: "Web Hosting"
---

```{r Clean workspace}
#| include: false

rm(list = ls())
```

```{r List all used packages}
#| include: false

packages <- c("downlit", "xml2")
```


```{r Install missing packages}
#| include: false

install.packages(setdiff(packages, rownames(installed.packages())))
```

```{r Load packages}
#| include: false

lapply(packages, require, character.only = TRUE)
```

## Introduction

There are many ways to host websites on the internet.  Below are some free options.

- A Quarto website can be published on on GitHub Pages for free.  Check [this GSheet](https://docs.google.com/spreadsheets/d/1efz-KlHgNicp8T8Kzt5ELlX6i0pvwFerosTHLgGwW_Y/preview) for options.

## Github Actions & R Dependencies

The [TidyTuesday GitHub Action build](https://github.com/hashcx/TidyTuesday/actions/runs/29706448783/job/88244170879) shows an error when trying restore the `magick 2.9.1` package because it depends on `libMagick++-6.Q16.so.9` (a system dependecy) that could not be found.

```
✔ magick 2.9.1                             [installed binary]
Error: code 1]
/opt/R/4.4.2/lib/R/bin/R --vanilla -s -f '/tmp/Rtmp7xYRF6/renv-install-179870a6fe78.R'
================================================================================

Error in dyn.load(file, DLLpath = DLLpath, ...) : 
  unable to load shared object '/home/runner/work/TidyTuesday/TidyTuesday/renv/staging/1/magick/libs/magick.so':
  libMagick++-6.Q16.so.9: cannot open shared object file: No such file or directory
Calls: loadNamespace -> library.dynam -> dyn.load
Execution halted
Traceback (most recent calls last):
10: renv::restore()
 9: renv_restore_run_actions(project, diff, current, lockfile, rebuild, 
        strict, descriptions)
 8: renv_graph_install(descriptions)
 7: handle(pkg, list(success = success, output = output, elapsed = elapsed))
 6: renv_graph_install_finalize(entry$record, entry$prepared, installdir, 
        project, linkable)
 5: tryCatch(renv_install_test(package), error = function(err) {
        unlink(installpath, recursive = TRUE)
        stop(err)
    })
 4: tryCatchList(expr, classes, parentenv, handlers)
 3: tryCatchOne(expr, names, parentenv, handlers[[1L]])
 2: value[[3L]](cond)
 1: stop(err)
Execution halted
Error: Process completed with exit code 1.
```

The solution is to install this required system dependecy during the GitHub Action Workflow (see the [one for TidyTuesday](https://github.com/hashcx/TidyTuesday/blob/main/.github/workflows/publish.yml)) as follows:

```
      - name: Install system dependencies
        run: |
          sudo apt-get update
          sudo apt-get install -y \
            libcurl4-openssl-dev \
            libssl-dev \
            libxml2-dev \
            libfontconfig1-dev \
            libharfbuzz-dev \
            libfribidi-dev \
            libfreetype6-dev \
            libpng-dev \
            libtiff5-dev \
            libjpeg-dev \
            libmagick++-dev
```
