# R/Rmd/qmd Files

It is advisable to perform the following step at the beginning of each code file.  The example code chuncks are for the R programming language.

## 1. Create Project

When wanting to write R code, create a project then add R/Rmd/qmd files into it instead of only creating a single file. This will allow saving the workspace settings.



## 2. Clean Workspace

Always start by clearing the workspace to ensure objects created in other files are not used in the current file by using the code shown blew.  This can be done manually in RStudio: Environment window -> Broom icon.

```{r}
#| eval: false

rm(list = ls())
```


## 3. Insall & Load Packages Automatically

Although people may not like installing packages on their machines automatically for different reasons, I prefer this route for myself because I use multiple machines and install packages one at a time (after the code breaks multiple time because of the missing packages) is annoying.

Step 1: Store all needed packages to a variables:

```{r}
#| eval: false

packages <- c("here", "tidyverse", "janitor")
```


Step 2: Install missing packages, if any

```{r}
#| eval: false

install.packages(setdiff(packages, rownames(installed.packages())))

```

Step 3: Load packages in one go


```{r Load Packages}
#| eval: false

lapply(packages, require, character.only = TRUE)
```

